Composable Concurrency Models

### 2016-10-20 paper/paper.tex
Vomited out some stuff about communicating threads

Conceptually, STM simplifies concurrency because it allows a transaction to be thought of as a single strictly serializable operation. A thread cannot observe changes made to other threads while a transaction is in progress, nor can other threads observe modifications by that thread until the transaction is completed. Only when a transaction completes successfully will changes will become visible to other threads.

@@

Instead of sharing memory, some concurrency models restrict operations to private memory. Threads communicate strictly by message passing, which avoids race conditions. Communicating sequential processes (CSP), one of the oldest communicating thread models, describes systems in terms of independent processes that communicate through predefined channels~\cite{Hoare1978}.

@@

@@

>>>>

Conceptually, STM simplifies concurrency because it allows a transaction to be thought of as a single strictly serializable operation. A thread cannot observe changes made to other threads while a transaction is in progress, nor can other threads observe modifications by that thread until the transaction is completed. Only when a transaction completes successfully will changes will become visible to other threads. Practically, STM is useful in any situation in which a shared object needs to be accessed and modified by multiple threads~\cite{Swalens2014}.

@@

Other concurrently models avoid the use of shared memory (and the problems that arise from doing so) by restricting threads to private memory. Threads communicate strictly by message passing, which avoids race conditions. A variety of different communicating thread models exist and have long been a solution to describing concurrent operations. Practical use cases for communicating threads include communication with external systems or running an event loop~\cite{Swalens2014}.

Communicating sequential processes (CSP), one of the oldest communicating thread models, describes systems in terms of independent processes that communicate through predefined channels~\cite{Hoare1978}. CSP is notable in that messages are passed synchronously; that is, a sending process will block until a complementary operation is executed on the receiving process~\cite{Swalens2014}.

@@

Shared state can also be represented by communicating threads. The agent model, for instance, works similarly to atomic references. A state wrapped by an agent can be modified by a message that sends an updated state. The value can be accessed by a dereferencing operation that reads the current value from the agent~\cite{Swalens2014}.

@@

This section may be unnecessary. There's already a lot of overlapping material in the background section that could be made more comprehensive.
